Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-07-02 ms.tex
changing some omega to -i\gamma --- need to go through and make sure variables are consistent
Units for Eq. 30, discussion of oscillations in Jsoln plot, and derivation of sigma_tp

\subsection{Summary}

@@

The diffusion equation for photons escaping a uniform sphere of gas is a function of time, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}. To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found. For simplicity a $J=0$ boundary condition will be used, which is expected to be a decent approximation for $\tau_0 \gg 1$.

@@

The source is changed to the form
\be
j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) .
\label{eq:jem2}
\ee
where $E$ is the energy emitted in the impulse at time $t=0$. 
The resulting equation for $J(r,\sigma,t)$ is
\be
-3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
\label{eq:diffusion_eqn}
\ee
We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is
\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
\ee
with
\be
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee
Plugging this in to Eq. \ref{eq:diffusion_eqn} and evaluating the integral, we obtain
\be \label{eq:diffusion_plugged_in}
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee
This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$. We start with a treatment of the boundary conditions. At $\sigma=\sigma_s$ continuity must be enforced in $J$ 
\be \label{eq:matching_condition_1}
J_+ = J_-
\ee
and the discontinuity in $dJ/d\sigma$  must be
\be \label{matching_condition_2}
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
\ee
according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
\be \label{eq:diffusion_at_large_sigma}
\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
\ee
which has solutions 
\be
J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}
\ee
and thus
\be \label{eq:single_j_derivative}
\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J
\ee
where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$. Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$ to isolate the solution that increases exponentially toward the line center. Initial values for integration are obtained by setting $J=1$ in Eq. \ref{eq:single_j_derivative}. This gives $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$. By enforcing the matching conditions Eqs. \ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained for all photon frequencies $\sigma$. Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.

Let us define the damping time to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions. There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$. Here, $m$ is an index that represents individual frequency eigenmodes, as opposed to $n$ which represents the spatial mode number. Near these frequencies, the solution will have the form 
\be
J(n,\sigma,\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
\ee
Obtaining the values of these eigenfrequencies and their corresponding eigenfunctions $J_{nm}(\sigma)$ allows us to obtain the contribution of this mode to the total solution via contour integration. 
\be
J(r,\sigma,t) & = &  j_0(\kappa_n r)  \int \frac{d\omega}{2\pi} e^{-\gamma t}J(n,\sigma,\gamma)
\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Here we have closed the integral along the $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer. The contribution from the semi-circle at infinity is zero. Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
\be \label{eq:Jrsigmat}
J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Beginning with Eq. \ref{eq:Jrsigmat}, we use the derivative
\be
\frac{dj_0(\kappa_n r)}{dr} \rfloor_R & =& \frac{d}{dr}  \rfloor_R \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)
=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)\rfloor_R
\nonumber \\ & = & \frac{(-1)^n}{R},
\ee
to obtain the flux at the surface, which is
\be
F(R,\sigma,t) & =& - \frac{4\pi}{3k\phi} \frac{dJ(R,\sigma,t)}{dr} 
= - \frac{4\pi}{3k\phi R}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Multiplying by $4\pi R^2$ gives the energy per time per frequency
\be
\frac{dE}{dtd\nu} & = & - \frac{16\pi^2 R}{3k\phi}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\label{eq:dEdtdnu}
\ee
Integrating this over time yields a factor $-1/\gamma_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
\be
1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
\ee
This non-trivial expression provides a check on the values of $\gamma_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
\be
1 & =& \sum_{nm} P_{nm},
\label{eq:sumrule}
\ee
where the contribution of each eigenfunction is
\be
P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
\ee
These coefficients can have either sign depending on the value of $n$.

@@

We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\omega_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$. To do this, we generalize the equations for eigenfunctions $J(n,\sigma,\omega)$ to allow $\omega = \omega_r + i \omega_i$, where previously we were using the real frequency $\omega_r$ and now we use the imaginary part $\omega_i$ (hereafter referred to as simply $\chi$). A resonant response in $J(n,\sigma,\omega)$ is produced for $\omega_r=0$ and special values of $\chi<0$.

To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,\omega)$ over $\sigma$ in array form. Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\chi$. In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\chi_{j-1},\chi_{j+1})$. We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in imaginary frequency $\omega_i$.

In the solve step, we evaluate the eigenfunctions at the points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$. A ``guess'' at the correct eigenvalue $\chi_{nm}$ can be calculated from
\be
\chi_{\rm guess} &=& \frac{a\chi_{j-1} - \chi_{j+1}}{a - 1}
\ee
where
\be
a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\chi_{j+1}-\chi_{j}}{\chi_{j-1}-\chi_{j}}\right).
\ee
This is repeated, replacing former points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ with closer estimates while the size of the response grows as we approach the resonance. Given a sufficiently accurate eigenvalue $\chi_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$. We can write down an approximate expression for the response near the resonances as
\be
J(n,\sigma,\chi) & \simeq & \frac{J_{nm}(\sigma)}{\chi-\chi_{nm}} + C(\sigma),
\ee
where $C(\sigma)$ is weakly dependent on $\chi$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
\be
J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2)& = &  \frac{J_{nm}(\sigma)}{\chi_1-\chi_{nm}} -  \frac{J_{nm}(\sigma)}{\chi_2-\chi_{nm}}
\ee
where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
\be
J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2) }{ 1/(\chi_1-\chi_{nm}) - 1/(\chi_2-\chi_{nm})}.
\ee
\begin{figure}
    \centering
    \includegraphics{Jsoln_n1_m100.pdf}
    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$. Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity. The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
    \label{fig:jsoln}
\end{figure}
A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig. \ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$. Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.

@@

\subsection{Results}

%\begin{figure}
%\plotone{KT_Eri.pdf}
%\caption{The Swift/XRT X-ray light curve for the first year after 
%outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
%328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
%the component figures (6) are available in the Figure Set. Note that
%these components that are {\bf not} shown in the compiled pdf. The figure
%set consists of the same figures as shown in Figure \ref{fig:pyramid}. 
%The example figure shown for figure sets can be one component or many. 
%\label{fig:fig4}}
%\end{figure}

>>>>

@@

The diffusion equation for photons escaping a uniform sphere of gas is a function of time, which was ignored in the steady-state calculations in Section \ref{sec:steadystate}. To obtain the radiative intensity $I=dE/(dAdtd\Omega d\nu)$ of a fluid that is dynamic on timescales shorter than the light-crossing time $t_{\rm lc} = R/c$, the time-dependent response to an impulse is found. This allows the distribution of photon escape times (the ``wait time distribution'') to be characterized and fit for efficient sampling. For simplicity a $J=0$ boundary condition will be used in the following derivations, which is expected to be a decent approximation for $\tau_0 \gg 1$.

@@

The source is changed to the form
\be
j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) ,
\label{eq:jem2}
\ee
which is a standard expression for emissivity in CGS units where $E$ is the energy emitted in the impulse at time $t=0$. 
The resulting equation for $J(r,\sigma,t)$ is
\be
-3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta^3(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
\label{eq:diffusion_eqn}
\ee
We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is
\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
\ee
with
\be \label{eq:jnsigmaomega}
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee
Eq. \ref{eq:jrsigmat_expansion} is the standard specific mean intensity in units of energy per unit area per unit time per Hertz, expressed here in CGS units. Though the frequency variable used here is $\sigma$, the specific mean intensity is to be integrated with respect to $\nu$. Eq. \ref{eq:jnsigmaomega} is in the same units, but with an additional unit of time in the numerator as a result of the expansion. Plugging the expression for the eigenfunctions $J(n, \sigma, \omega)$ into the differential equation Eq. \ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
\be \label{eq:diffusion_plugged_in}
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee
This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$. We start with a treatment of the boundary conditions. At $\sigma=\sigma_s$ continuity must be enforced in $J$ 
\be \label{eq:matching_condition_1}
J_+ = J_-
\ee
and the discontinuity in $dJ/d\sigma$  must be
\be \label{matching_condition_2}
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
\ee
according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
\be \label{eq:diffusion_at_large_sigma}
\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
\ee
which has solutions 
\be
J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}
\ee
and thus
\be \label{eq:single_j_derivative}
\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J
\ee
where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$. Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$ to isolate the solution that increases exponentially toward the line center. Initial values for integration are obtained by setting $J=1$ in Eq. \ref{eq:single_j_derivative}. This gives $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$. By enforcing the matching conditions Eqs. \ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained for all photon frequencies $\sigma$. Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.

Let us define the damping time to be $\gamma \equiv i\omega$, which is real-valued and positive for damped solutions. There are certain values of $\gamma$ for which a resonant response is produced which we will call $\gamma_{nm}$. Here, $m$ is an index that represents individual frequency eigenmodes, as opposed to $n$ which represents the spatial mode number. Near these frequencies, the solution will have the form 
\be
J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
\ee
Obtaining the values of these eigenfrequencies and their corresponding eigenfunctions $J_{nm}(\sigma)$ allows us to obtain the contribution of this mode to the total solution via contour integration. 
\be
J(r,\sigma,t) & = &  -j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t}J(n,\sigma,-i\gamma)
\nonumber \\ & \simeq & j_0(\kappa_n r)  \int \frac{d\gamma}{2\pi i} e^{-\gamma t} \frac{ J_{nm}(\sigma) }{\gamma - \gamma_{nm}} 
\nonumber \\ & \simeq & j_0(\kappa_n r)  J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Here we have closed the integral along the imaginary $\gamma$ axis by a semi-circle at infinity, using the residue theorem to obtain the answer. The contribution from the semi-circle at infinity is zero. Summing over all spatial eigenmodes $n$ and over all temporal eigenmodes $m$ for a given $n$, we get the final form of the result
\be \label{eq:Jrsigmat}
J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_m J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Beginning with Eq. \ref{eq:Jrsigmat}, we use the derivative
\be
\frac{dj_0(\kappa_n r)}{dr} \rfloor_R & =& \frac{d}{dr}  \rfloor_R \left( \frac{\sin(\kappa_n r)}{\kappa_n r} \right)
=  \left( \frac{\cos(\kappa_n R)}{R} - \frac{\sin(\kappa_n R)}{\kappa_n R^2} \right)\rfloor_R
\nonumber \\ & = & \frac{(-1)^n}{R},
\ee
to obtain the flux at the surface, which is
\be
F(R,\sigma,t) & =& - \frac{4\pi}{3k\phi} \frac{dJ(R,\sigma,t)}{dr} 
= - \frac{4\pi}{3k\phi R}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Multiplying by $4\pi R^2$ gives the energy per time per frequency
\be
\frac{dE}{dtd\nu} & = & - \frac{16\pi^2 R}{3k\phi}  \sum_{nm} (-1)^n J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\label{eq:dEdtdnu}
\ee
Integrating this over time yields a factor $-1/\gamma_{nm}$, and over $d\nu = \sqrt{3/2} \Delta^2 \phi d\sigma$, a ``sum rule" results
\be
1 & = &  \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE} \sum_{nm} (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
\ee
This non-trivial expression provides a check on the values of $\gamma_{nm}$ and the functions $J_{nm}(\sigma)$. This expression can also be written as
\be
1 & =& \sum_{nm} P_{nm},
\label{eq:sumrule}
\ee
where the contribution of each eigenfunction is
\be
P_{nm} & \equiv & \sqrt{ \frac{3}{2} } \frac{16\pi^2R\Delta^2}{3kE}  (-1)^n \gamma_{nm}^{-1} \int d\sigma J_{nm}(\sigma).
\ee
These coefficients can have either sign depending on the value of $n$.

@@

We seek now to tabulate all eigenmodes $J_{nm}(\sigma)$ and eigenfrequencies $\gamma_{nm}$ for all spatial $n$ and for all eigenmodes $m$ at that given $n$. A resonant response in $J(n,\sigma,-i\gamma)$ is produced when the imaginary frequency is negative and has no real component. To measure the size of the response to detect where resonances occur, we sum the absolute value of $J(n,\sigma,-i\gamma)$ over $\sigma$ in array form. Call this response $f$, and use the index $j$ to represent the value of the response at discrete points over a range of $\gamma$. In places where $f_j > f_{j-1}$ and $f_j>f_{j+1}$, we have bounded a resonance that occurs in the interval $(\gamma_{j-1},\gamma_{j+1})$. We then call the ``solve'' step to hone in on the eigenvalue before continuing the sweep in $\gamma$. In the solve step, we evaluate the eigenfunctions at the points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$. A ``guess'' at the correct eigenvalue $\gamma_{nm}$ can be calculated from
\be
\gamma_{\rm guess} &=& \frac{a\gamma_{j-1} - \gamma_{j+1}}{a - 1}
\ee
where
\be
a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\gamma_{j+1}-\gamma_{j}}{\gamma_{j-1}-\gamma_{j}}\right).
\ee
This is repeated by replacing former points $(\gamma_{j-1},\gamma_{j},\gamma_{j+1})$ with closer estimates while the size of the response grows as the resonance is approached. Given a sufficiently accurate eigenvalue $\gamma_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$. We can write down an approximate expression for the response near the resonances as
\be
J(n,\sigma,-i\gamma) & \simeq & \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma} + C(\sigma),
\ee
where $C(\sigma)$ is weakly dependent on $\gamma$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
\be
J(n,\sigma,-i\gamma_1)  - J(n,\sigma,-i\gamma_2)& = &  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_1} -  \frac{J_{nm}(\sigma)}{\gamma_{nm}-\gamma_2}
\ee
where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
\be
J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\gamma_1)  - J(n,\sigma,\gamma_2) }{ 1/(\gamma_{nm}-\gamma_1) - 1/(\gamma_{nm}-\gamma_2)}.
\ee
\begin{figure}
    \centering
    \includegraphics{Jsoln_n1_m100.pdf}
    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$. Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity. The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
    \label{fig:jsoln}
\end{figure}
A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig. \ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$. Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms. The oscillations of various modes must cancel perfectly to recreate the form of the solution in Eq. \ref{eq:Jrsigmat}, so many modes $m$ and $n$ are required for sufficient numerical precision in the final result. Too few (or imprecisely-calculated) modes creates ``ringing'' in the function that indicates the presence of imperfect cancellations in the positive and negative contributions of individual poles.

A single eigenmode $J_{nm}(\sigma)$ is oscillatory out to some turning point, $\sigma_{tp}$, at which point the function becomes evanescent. The location of the turning point can be found by ignoring the delta-function discontinuity at the source frequency $\sigma_s$ in Eq. \ref{eq:diffusion_plugged_in} and re-examining the resulting homogeneous differential equation. We obtain
\be
\frac{d^2J}{d\sigma^2} & = & \left[ \left( \frac{\kappa_n \Delta }{k} \right)^2 - \frac{3\phi \gamma\Delta^2}{ck}\right] J
\ee
where the line profile can be written approximately as $\phi = (2a/\pi)^{1/3}/(3 \Delta |\sigma|^{2/3})$. When the coefficient on the right hand side is positive, exponential growth or decay solutions are found (evanescence). This occurs on the line wings. When the coefficient on the right hand side is negative, oscillatory solutions are found (propagation), which occurs in the line core. The boundary between propagation and evanescence occurs at the turning point, given by
\be
\sigma_{tp} & = & \sqrt{\frac{2a}{\pi}}\left( \frac{k \gamma}{ \kappa_n^2 c \Delta} \right)^{3/2}
\ee
Thus, to ensure accuracy in the final sum of Eq. \ref{eq:Jrsigmat}, the bounds of $\sigma$ must be set sufficiently far outside of $\sigma_{tp}$ such that the function is small at the edges. The scale of an $e$-folding in $J_{nm}(\sigma)$ is $k/(\kappa_n \Delta) = \tau_0 / (\sqrt{\pi} n)$, so a grid of $\sigma$ is chosen that spans a large enough number of $e$-foldings that no oscillatory behavior is present at the boundaries of the calculation.

@@

\section{Summary and Conclusions}

The time-dependence of the problem can also be solved to
